Tables

### 2019-11-12 code/tables.rmd
Updated Table 1 for clarity

## Table 1
### Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
```{r effect-size-heterogeneity-table, cache = TRUE}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")

rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
rooted_relabilities <- data.frame(rel, rooted_relabilities)

rooted_relabilities %>% knitr::kable(booktabs = T, col.names = c("", "$\\rho_{xy}$ = 0", "$\\rho_{xy}$ = .3", "$\\rho_{xy}$ = .5"), escape = FALSE, digits = 2) %>% 
  kable_styling(position = "left") %>% 
  row_spec(3, hline_after = T)

```
*Note:* Values in cells are observed effect sizes arising from the true effect size $\rho_{xy}$ and measurement reliabilites $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ when sample size is infinite. Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06

>>>>

## Table 1
### Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
```{r effect-size-heterogeneity-table, cache = TRUE}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
ma <- c("I: $\\mu = 0$", "II: $\\mu = .3$", "III: $\\mu = .5$")

rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
devs <- apply(rooted_relabilities, 2, sd)
table1 <- data.frame(ma, t(rooted_relabilities), devs)

table1 %>% knitr::kable(booktabs = T, col.names = c("Meta-Analysis", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)"), escape = FALSE, digits = 2) %>% 
  kable_styling(position = "left") %>% 
  add_header_above(c(" " = 1, "Study 1"= 1, "Study 2" = 1, "Study 3" = 1)) %>% 
  add_header_above(c(" " = 1, "Observed effect sizes" = 3))

#alternative inversed table 1
# table1b <- t(table1)[2:5,]
# studies <- c("Study 1: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "Study 2: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "Study 3: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)")
# table1b <- cbind(studies, table1b)
# rownames(table1b) <- NULL
# 
# table1b %>% knitr::kable(booktabs = T, col.names = c("Study and Measurement Error", "I: $\\mu = 0$", "II: $\\mu = .3$", "III: $\\mu = .5$"), escape = FALSE, digits = 2) %>% 
#   add_header_above(c(" " = 1, "Meta-Analysis" = 3)) %>% 
#   add_header_above(c(" " = 1, "Observed effect sizes" = 3)) %>% 
#   row_spec(3, hline_after = TRUE)
```
*Note:* The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ and the true effect size $\rho_{xy}$  when sample size is infinite. SD(ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III; equivalent to heterogeneity given infinite sample sizes. Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06
